Discriminative Sensing Based on Signal Processing

### 2017-10-23 docs/thesis/chapters/2_pca_svm_cfa/pca_svm_cfa.tex
section 2.3

\begin{figure}[h!]
     \centering 
     \includegraphics[height=10cm, width=10cm]{figures/ch2/raw_igovti_covariance}
     \caption{Covariance matrix of iGovTI questions.}
     \label{fig:ch2_fig1}
\end{figure}

The correlation matrix of 201 questions reveals

>>>>

\begin{figure}[h!]
     \centering 
     \includegraphics[height=10cm, width=10cm]{figures/ch2/raw_igovti_covariance.eps}
     \caption{Covariance matrix of iGovTI questions.}
     \label{fig:ch2_fig1}
\end{figure}

Figure \ref{fig:ch2_fig1} presents the matrix presents of 201 questions of iGovTI, where is possible to observe low covariance for the majority questions and high variance for just a few variables. The low covariance reveals
